**Blue Whiting**

### 2023-02-08 Rmd/condMac.Rmd
with figs as "A.x"

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)
opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/mac/cond/",
               fig.path  ="../tex/figs/mac/cond",
               fig.width =8,
               fig.height=6,
               dev       ="png")
iFig=0
iTab=0
```

@@

**Figure `r iFig=iFig+1; iFig`** Time series

@@

**Figure `r iFig=iFig+1; iFig`** Mass-at-age

@@

**Figure `r iFig=iFig+1; iFig`** Maturity-at-age

@@

**Figure `r iFig=iFig+1; iFig`** M-at-age

@@

**Figure `r iFig=iFig+1; iFig`** Mass-at-age, summary

@@

**Figure `r iFig=iFig+1; iFig`** Mass-at-age v Biomass

@@

**Figure `r iFig=iFig+1; iFig`** Maturity-at-age, summary

@@

**Figure `r iFig=iFig+1; iFig`** Maturity-at-age v Biomass

@@

**Figure `r iFig=iFig+1; iFig`** Maturity-at-age v mass-at-age  (k=`r par$par[1]` $W_{50}$=`r par$par[2]`)

>>>>

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)
opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/mac/cond/",
               fig.path  ="../tex/figs/mac/cond/",
               fig.width =8,
               fig.height=6,
               dev       ="png")
iFig=0
iTab=0
```

@@

**Figure A.`r iFig=iFig+1; iFig`** Time series

@@

**Figure A.`r iFig=iFig+1; iFig`** Mass-at-age

@@

**Figure A.`r iFig=iFig+1; iFig`** Maturity-at-age

@@

**Figure A.`r iFig=iFig+1; iFig`** M-at-age

@@

**Figure A.`r iFig=iFig+1; iFig`** Mass-at-age, summary

@@

**Figure A.`r iFig=iFig+1; iFig`** Mass-at-age v Biomass

@@

**Figure A.`r iFig=iFig+1; iFig`** Maturity-at-age, summary

@@

**Figure A.`r iFig=iFig+1; iFig`** Maturity-at-age v Biomass

@@

**Figure A.`r iFig=iFig+1; iFig`** Maturity-at-age v mass-at-age  (k=`r par$par[1]` $W_{50}$=`r par$par[2]`)

### 2023-02-08 Rmd/condWhb.Rmd
with figs as "A.x"

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)
opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/whb/cond/",
               fig.path  ="../tex/figs/whb/cond",
               fig.width =8,
               fig.height=6,
               dev       ="png")
iFig=0
iTab=0
```

>>>>

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# getwd()
library(knitr)
opts_chunk$set(cache     =TRUE, 
               comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE, 
               eval      =TRUE,cache   =TRUE,
               cache.path="../cache/whb/cond/",
               fig.path  ="../tex/figs/whb/cond/",
               fig.width =8,
               fig.height=6,
               dev       ="png")
iFig=0
iTab=0
```
